supplmental

### 2019-12-31 paper_stats.Rmd
tables

```{r table1_describe}

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>%
  as.matrix() %>%
  kable()

@@

Table 2. Blood pressure outcomes
```{r}

@@

  full_join(means_df, difs_df, by = "Outcome") %>%
    select(Outcome, everything()) %>%
    as.matrix() %>%
    pander()

>>>>

```{r table1_describe, results = "asis"}

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>%
  kable()

@@

Table 2. Blood pressure outcomes
```{r results = "asis"}

@@

  full_join(means_df, difs_df, by = "Outcome") %>%
    select(Outcome, everything()) %>%
    pander()
